---
title: "p8105_Hw6_Ec3342"
author: "Ekta Chaudhary"
date: "14/11/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
library(modelr)
library(p8105.datasets)
```
#Reading the data set and tidying the data. Converted the numeric to factor variables. Removed pnumlbw, pnumsga, malform as these variables had a value of 0 for all the observations.So, there was no point keeping these variables in the dataset.

```{r}
baby_data = read_csv(file = "./data/birthweight.csv") %>%
  janitor::clean_names() %>%
  mutate(
    babysex = as.factor(babysex),
    frace = as.factor(frace),
    malform = as.factor(malform),
    mrace = as.factor(mrace)
  ) %>%
  select(-pnumlbw, -pnumsga, -malform)
```

#Checking if there are any missing variables. After running the code, we see that there are no missing variables; Therefore, we do not have to do anything more to clean the data.

```{r}
filter_all(
  baby_data, any_vars(is.na(.))
)
```
#Propose a regression model for birthweight. As the outcome is continuous, we can fit a linear regression model. 

```{r}

model_1 = lm(bwt ~ gaweeks + babysex + momage + mrace  + wtgain + smoken, data = baby_data)
model_1 %>% 
  broom::tidy() 

```

#Show a plot of model residuals against fitted values – use add_predictions and add_residuals in making this plot.

```{r}

baby_data %>% 
  modelr::add_predictions(model_1) %>% 
  modelr::add_residuals(model_1) %>% 
  ggplot(aes(x = pred, y = resid)) + geom_point() +
  labs(x = "Predicted value", 
       y = "Residual")

```

#Compare your model to two others:

#Using cross validation methods to compare my model with two other models:

```{r}

model_2 = lm(bwt ~ blength + gaweeks, data = baby_data) # Using length at birth and gestational age as predictors (main effects only)

model_3 = lm(bwt ~ bhead + babysex + blength + bhead * babysex * blength, data = baby_data) #using head circumference, length, sex, and all interactions (including the three-way interaction) between these

```
Cross validation

```{r}
set.seed(1)

cv_df =
  crossv_mc(baby_data, 100) %>% 
  mutate(
    train = map(
      train, as_tibble),
         test = map(
           test, as_tibble)
    )
```

```{r}

cross_validation = 
  cv_df %>% 
  mutate(
    model_2 = map(
      train, ~ lm(bwt ~ blength + gaweeks, data = .x)
      ),
    model_3 = map(
      train, ~ lm(bwt ~ bhead + babysex + blength + bhead * babysex * blength, data = .x)
      ),
    model_1 = map(
      train, ~ lm(bwt ~ gaweeks + babysex + momage + mrace  + wtgain + smoken, data = .x)
      )
    ) %>% 
  mutate(
    rmse_model_2 = map2_dbl(
      model_2, test, ~ rmse(model = .x, data = .y)
      ),
    rmse_model_3 = map2_dbl(
      model_3, test, ~ rmse(model = .x, data = .y)
      ),
    rmse_model_1 = map2_dbl(
      model_1, test, ~ rmse(model = .x, data = .y)
      )
    )
  
```

```{r}
cross_validation %>% 
  select(
    starts_with("rmse")
    ) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
   mutate(
         model = fct_relevel(model, "model_1","model_2","model_3")
         ) %>% 
  ggplot(aes(x = model, y = rmse, fill = model)) +
  geom_violin() + 
  labs(
    title = "Distribution of Prediction Error Across Models",
    x = "Model",
    y = "RMSE"
  )
```
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

