---
title: "p8105_Hw6_Ec3342"
author: "Ekta Chaudhary"
date: "14/11/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
library(modelr)
library(p8105.datasets)
```
# Question 1

* Reading the data set and tidying the data. Converted the numeric to factor variables. Removed pnumlbw, pnumsga, malform as these variables had a value of 0 for all the observations.So, there was no point keeping these variables in the dataset.

```{r}

baby_data = read_csv(file = "./data/birthweight.csv") %>%
  janitor::clean_names() %>%
  mutate(
    babysex = as.factor(babysex),
    frace = as.factor(frace),
    malform = as.factor(malform),
    mrace = as.factor(mrace)
  ) %>%
  select(-pnumlbw, -pnumsga, -malform)

```

* Checking if there are any missing variables. After running the code, we see that there are no missing variables; Therefore, we do not have to do anything more to clean the data.

```{r}

filter_all(
  baby_data, any_vars(is.na(.))
)

```

* Propose a regression model for birthweight.

As the outcome (baby's birthweight) is continuous, we can fit a linear regression model. 

Baby's birthweight can be associated with gestational age in weeks, baby's sex, mom's age, mom's race, mom's weight gain and average number of cigarettes smoked per day during pregnancy as these variables can be associated with baby's birthweight.

```{r}

model_1 = lm(bwt ~ gaweeks + babysex + momage + mrace  + wtgain + smoken, data = baby_data)
model_1 %>% 
  broom::tidy() 

```

* Show a plot of model residuals against fitted values – use add_predictions and add_residuals in making this plot.

```{r}

baby_data %>% 
  modelr::add_predictions(model_1) %>% 
  modelr::add_residuals(model_1) %>% 
  ggplot(aes(x = pred, y = resid)) + geom_point() + 
  labs(x = "Predicted value", 
       y = "Residual")

```

* Compare your model to two others:

Using cross validation methods to compare my model with two other models:

```{r}

model_2 = lm(bwt ~ blength + gaweeks, data = baby_data) 
#In model 2, using length at birth and gestational age as predictors (main effects only)

model_3 = lm(bwt ~ bhead + babysex + blength + bhead * babysex * blength, data = baby_data) 
#In model 3, using head circumference, length, sex, and all interactions (including the three-way interaction) between these

```

* Make this comparison in terms of the cross-validated prediction error; use crossv_mc and functions in purrr as appropriate.

```{r}
set.seed(1)

cv_df =
  crossv_mc(baby_data, 100) %>% 
  mutate(
    train = map(
      train, as_tibble),
         test = map(
           test, as_tibble)
    )
```

```{r}

cross_validation = 
  cv_df %>% 
  mutate(
    model_1 = map(
      train, ~ lm(bwt ~ gaweeks + babysex + momage + mrace  + wtgain + smoken, data = .x)
      ),
    model_2 = map(
      train, ~ lm(bwt ~ blength + gaweeks, data = .x)
      ),
    model_3 = map(
      train, ~ lm(bwt ~ bhead + babysex + blength + bhead * babysex * blength, data = .x)
      )
    ) %>% 
  mutate(
    rmse_model_2 = map2_dbl(
      model_2, test, ~ rmse(model = .x, data = .y)
      ),
    rmse_model_3 = map2_dbl(
      model_3, test, ~ rmse(model = .x, data = .y)
      ),
    rmse_model_1 = map2_dbl(
      model_1, test, ~ rmse(model = .x, data = .y)
      )
    )
  
```

```{r}

cross_validation %>% 
  select(
    starts_with("rmse")
    ) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
   mutate(
         model = fct_relevel(model, "model_1","model_2","model_3")
         ) %>% 
  ggplot(aes(x = model, y = rmse, fill = model)) +
  geom_violin() + 
  labs(
    title = "Distribution of Prediction Error Across Models",
    x = "Model",
    y = "RMSE"
  )

```

**Based on the violen plots above, we can see that the _third model_ i.e. the model with three way interaction is the best model because it has the minimum RMSE.**  


# Question 2

* The code chunk below (adapted from the course website) will download these data.

```{r}

weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())

```

We’ll focus on a simple linear regression with tmax as the response and tmin as the predictor, and are interested in the distribution of two quantities estimated from these data.
Use 5000 bootstrap samples and, for each bootstrap sample, produce estimates of these two quantities. Plot the distribution of your estimates, and describe these in words. 
Using the 5000 bootstrap estimates, identify the 2.5% and 97.5% quantiles to provide a 95% confidence interval for r̂2 and log(β̂0∗β̂1)

* The output from the code below shows results from fitting simple linear regression

```{r}

lm(tmax ~ tmin, data = weather_df) %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)

```

* Now writing a function to generate our bootstrap samples. 

```{r}

boot_sample = function(weather_df) {
  sample_frac(weather_df, replace = TRUE)
}

```

* We should also do a quick check to see if this is working.

```{r}

boot_sample(weather_df) %>% 
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point(alpha = .5) +
  stat_smooth(method = "lm")

```
* Doing this for 5000 bootstrap samples

```{r}

boot_straps = 
 data_frame(
    strap_number = 1:5000,
    strap_sample = rerun(5000, boot_sample(weather_df))
  )
```

* Analyzing bootstrap samples to produce estimates of r_squared

```{r}

bootstrap_results = 
  boot_straps %>% 
  mutate(
    models = map(strap_sample, ~lm(tmax ~ tmin, data = .x)
                 ),
    results = map(models, broom::glance),
    estimate = map(models, broom::tidy)
    ) %>% 
  select(-strap_sample, -models) %>% 
  unnest() %>%
  select(
    strap_number, r.squared, term, estimate
  ) %>%
  pivot_wider(
    names_from = "term",
    values_from = "estimate"
  ) %>%
  janitor::clean_names() 
#Plotting a distribution of the estimates
bootstrap_results %>% 
  ggplot(aes(x = r_squared)) + 
  geom_density() 

```

* Using the 5000 bootstrap estimates, identify the 2.5% and 97.5% quantiles to provide a 95% confidence interval for r̂2

```{r}

bootstrap_results %>% 
  pull(r_squared) %>% 
quantile(., probs = c(0.025, 0.975), na.rm = TRUE)

```
The 2.5% and 97.5% quantiles are 0.894 and 0.927 respectively.

* Analyzing bootstrap samples to produce estimates of log(β̂0∗β̂1)

```{r}

  bootstrap_results_2 =
  boot_straps %>% 
  mutate(
    models = map(strap_sample, ~lm(tmax ~ tmin, data = .x)
                 ),
    results = map(models, broom::glance),
    estimate = map(models, broom::tidy)
    ) %>% 
  select(-strap_sample, -models) %>% 
  unnest() %>%
  select(
    strap_number, r.squared, term, estimate
  ) %>%
  pivot_wider(
    names_from = "term",
    values_from = "estimate"
  ) %>%
  janitor::clean_names() %>%
  mutate(
    log_beta = log(intercept*tmin)
    ) 
#Plotting a distribution of the estimates
bootstrap_results_2 %>% 
  ggplot(aes(x = log_beta)) + 
  geom_density()

```

* Using the 5000 bootstrap estimates, identify the 2.5% and 97.5% quantiles to provide a 95% confidence interval for log(β̂0∗β̂1)

```{r}

bootstrap_results_2 %>% 
  pull(log_beta) %>% 
quantile(., probs = c(0.025, 0.975), na.rm = TRUE) 

```
The 2.5% and 97.5% quantiles are 1.966 and 2.058 respectively.


